\TheTitle

### 2015-08-28 linvis.tex
Fix: Spacing on verbatim section
Edits: Makefile, related work, introduction, and citations
Added citations.bib to the makefile

Added information to the related and introduction section.

Added citations for the related works.

\begin{figure}
	\centering
	\includegraphics[width=0.47\textwidth]{figures/gitk.png}
	\caption{DAG view in Gitk}
	\label{fig:gitk}
\end{figure}

Git log, Gitk, and other similar tools only store the authored date of a
commit. A commit may be merged into the project at any time, regardless of when
the commit was authored, making date-range queries meaningless. Performing a
date-range query using these tools over the span of a release will contain
results that are for previous versions of the kernel or may not contain all
of the results for that kernel if patches were merged after the release date.

@@

All top-level merges to a given version of the kernel are merged between the
start and release date. Our tree construction allows us to use the top-level
merges to find all merges and commits that have an effect on a given version of
the kernel. The model allows us to better provide mechanisms for performing
date-range queries, providing access to all commits that have an effect on a
given release, even if the commit comes before the start date or after the
release date.

\section{Related Work}
To our knowledge, we know of no repository visualization systems using a
tree-based model. This may be due to the fact that more information is required
to generate the trees than what is stored by git. A server must sit and monitor
the repository as it changes over time. Many of the visualization tools are
designed for a general-purpose approach, where any repository is directly
usable without additional information. Polling for this additional information
makes the application specific to a single repository or project.

\subsection{Gitk}
Gitk, Gitg, and other similar git repository visualizing tools use the DAG as
the central organization model. For smaller projects, this model is sufficient
for providing meaningful information, but in larger projects like the Linux
kernel, the branches become too tangled and too deep to derive any meaning from
the DAG. The DAG model allows users to go to the next commit in the chain, go
to the previous commit in the chain, or jump to the parent merge. This suggest
that Gitk and similar tools are designed for users working with a bottom-to-top
approach. With this model, it is difficult for users to see what other commits
are involved with a given merge. Gitk only provides file information on
commits, as it is unable to quickly find all files edited by the commits within
a merge. It is up to the user to remember what files were edited in each of the
commits involved in a given merge. In some of the larger merges, some
containing over 1500 edited files, this task become nearly impossible.
% cid: 73287a43cc79ca06629a88d1a199cd283f42456a, 1800 commits, 1500 files
Other DAG visualization systems, like the GitHub viewer (\ref{fig:gitfail}),
are unable to provide a visualization for projects that are as large as the
kernel.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/github_viewer.png}
	\caption{Github Failure Message}
	\label{fig:gitfail}
\end{figure}

@@

\subsection{Treemap visualizer}
University of Maryland presented a treemap visualization
tool\footnote{\url{https://www.cs.umd.edu/hcil/millionvis/Treemap_Visualization_of_the_Linux_Kernel_2_5_33.html}},
pictured in figure \ref{fig:treemap}, for
displaying the file structure of a given version. Treemaps are good for
visualizing the topology of shallow, wide trees, making it a good candidate for
showing file systems. Treemaps are limited in what information can be
displayed. The information within the treemap does not provide clear insight on
what changes were made to the files in the given release, only providing
information on where the file is located within the file system.
File systems and the merge tree of the kernel share many similarities, in both
cases, they represent trees that are wide and shallow, suggesting that a
treemap could potentially work to visualize the commit and merge structure of
the kernel.

The treemap is unable to take into account multiple commits behind the same
merge with the same name. Commits and merges have an ordering in which they
were added to the kernel, which cannot be represented by a treemap, but is
important and can be used to assist in building the tree.

@@

Searching allows a user to filter commits and merges that are irrelevant.
The search mechanism breaks down the results by release version. A user can
further narrow down the search range using the commit date range. The commit
date refers to the date of the creation of the top-level merge. Commits and
merges that are returned may have a commit date beyond the given range if they
were merged to a top-level merge that is within the date range. A user may then
provide a search text, filtering on the author name, the commit id, or keyword
from the log. Any part of the author name may show up in the results, including
searching by email address. The commit ID must be specified from the first
character to the last character. For example, the commit
`c267548755a184ef97301071300c1739a564e135' is returned when the user searches
for a commit id of `c26' in the 3.10 Linux kernel.

@@

Our tool further enhances our understanding by immediately giving us the files
and modules that were edited. We are able to determine that three files,
``palamas-regulator.c'' had two lines added and two lines removed,
``dbx500-prcmu.c'' had 12 lines added and 12 lines removed, and ``core.c'' had
5 lines added and 2 lines removed. Finally, we are able to determine that only
the ``regulator'' module was modified in this merge and was modified by 5
commits.

@@

\subsection{Testing}
At this time, we have no evidence that our tool is able to improve the
work-flow of maintainers. We believe that the tool is able to improve the
work-flow and performance of maintainers because it provides cleaner mechanisms
of visualizing and presenting the commit information. It is able to provide
more relevant information, while removing information that is irrelevant to a
given module or set of merges.

@@

\bibliographystyle{plain}
\bibliography{citations}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.47\textwidth]{figures/gitk.png}
	\caption{A sample DAG view of commits from Linux in Gitk}
	\label{fig:gitk}
\end{figure}

Git log, Gitk, and other similar tools only store the name of the author, authored
date of a commit. A commit may be merged into the project at any time, regardless of
when the commit was authored, making date-range queries meaningless. Performing a
date-range query using these tools over the span of a release will contain results
that are for previous versions of the kernel or may not contain all of the results
for that kernel if patches were merged after the release date.

@@

All top-level merges to a given version of the kernel are merged between the
start and release date. The tree construction allows us to find all commits that are
related to a given release of the kernel regardless of the authorship date, allowing
our system to provide better mechanisms for performing date-range queries.

\section{Related Work}
To our knowledge, we know of no repository visualization systems that builds a tree
from the merge. CVS and svn construct trees; however, the root node for these trees
is the branch point. This may be due to the fact that more information is required
to generate the trees than what is stored by git. A server must sit and monitor the
repository as it changes over time. Many of the visualization tools are designed for
a general-purpose approach, where any repository is directly usable without
additional information. Polling for this additional information makes the
application specific to a single repository or project.

\subsection{Gitk}
Gitk, Gitg, and other similar git repository visualizing tools use the DAG as
the central organization model. For smaller projects, this model is sufficient
for providing meaningful information, but in larger projects like the Linux
kernel, the branches become too tangled and too deep to derive any meaning from
the DAG. The DAG model allows users to go to the next commit in the chain, go
to the previous commit in the chain, or jump to the parent merge. This suggest
that Gitk and similar tools are designed for users working from a given commit or
leaf-node toward the root.  With this model, it is difficult for users to see what
other commits are involved with a given merge. Gitk only provides file information
on commits, as it is unable to quickly aggregate the files and commits that are part
of a merge. It is up to the user to remember what files were edited in each of the
commits involved in a given merge. In some of the larger merges, some containing
over 1500 edited files, this task become nearly impossible.  % cid: 73287a43cc79ca06629a88d1a199cd283f42456a, 1800 commits, 1500 files 
Other DAG visualization systems, like the GitHub viewer (\ref{fig:gitfail}), are
unable to provide a visualization for projects that are as large as the kernel.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/github_viewer.png}
	\caption{Github Failure Message showing the DAG of the Linux Project}
	\label{fig:gitfail}
\end{figure}

@@

\subsection{Treemap visualizer}
University of Maryland presented a treemap visualization
tool\footnote{\url{https://www.cs.umd.edu/hcil/millionvis/Treemap_Visualization_of_the_Linux_Kernel_2_5_33.html}},
pictured in figure \ref{fig:treemap}, for
displaying the file structure of a given version of the kernel. Treemaps are good
for visualizing the topology of shallow, wide trees, making it a good candidate for
showing file systems. Treemaps are limited in what information can be displayed. The
information within the treemap does not provide clear insight on what changes were
made to the files in the given release, only providing information on where the file
is located within the file system.  File systems and the merge tree of the kernel
share many similarities, in both cases, they represent trees that are wide and
shallow, suggesting that a treemap could potentially work to visualize the commit
and merge structure of the kernel.

The treemap is unable to take into account multiple commits behind the same merge
with the same log preview message. Commits and merges have an ordering in which they
were added to the kernel, which cannot be represented by a treemap, but is important
and can be used to assist in building the tree.

@@

Searching allows a user to filter commits and merges that are irrelevant.
The search mechanism breaks down the results by release version. A user can
further narrow down the search range using the commit date range. The commit
date refers to the date of the creation of the top-level merge. Commits and
merges that are returned may have a commit date beyond the given range if they
were merged to a top-level merge that is within the date range. A user may then
provide a search text, filtering on the author name, the commit id, or keyword
from the log. Any part of the author name may show up in the results, including
searching by email address. The commit ID must be specified from the first
character to the last character. For example, the commit
`c267548755a184ef97301071300c1739a564e135' is returned when the user searches
for a commit id of `c26' in the 3.10 Linux kernel. We will use this commit for
showing each of the features of the tool.

@@

Our tool further enhances our understanding by immediately giving us the files
and modules that were edited in the branch. We are able to determine that three
files, ``palamas-regulator.c'' had two lines added and two lines removed,
``dbx500-prcmu.c'' had 12 lines added and 12 lines removed, and ``core.c'' had 5
lines added and 2 lines removed. Finally, we are able to determine that only the
``regulator'' module was modified in this merge and was modified by 5 commits.

@@

\subsection{Evaluation}
At this time, we have no evidence that our tool is able to improve the
work-flow of maintainers. We believe that the tool is able to improve the
work-flow and performance of maintainers because it provides cleaner mechanisms
of visualizing and presenting the commit information. It is able to provide
more relevant information, while removing information that is irrelevant to a
given module or set of merges.

@@

\nocite{*}
\bibliographystyle{plain}
\bibliography{citations}
